Knowledge \& the web: exercise session 6

### 2015-11-21 exercise_6/ex6.tex
update ex6.tex

\section{Rule learning}
One thing we tried was to learn classification rules from the training data.
Rule learning algorithms come with different options for several aspects of the algorithms. In the exercise session we experimented with two of these.\\
First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.\\
The first option resulted in the following rule set:
When evaluated on the test set, we got an accuracy of ?.
The second option resulted in this rule set:
\begin{itemize}

>>>>

\section{Rule learning}
One thing we tried was to learn classification rules from the training data.
Rule learning algorithms come with different options for several aspects of the algorithms. In the exercise session we experimented with two of these.\\
First, for choosing the conditions of a classification rule, there are two options: one is to add to the rule the condition which increases the accuracy the most, another is to add to the rule the condition which increases the information gain the most.\\
The first option resulted in a rule set consisting of 363 rules which clearly overfitted the training data.
The second option resulted in this rule set:
\begin{itemize}
